\LARGE\singlespacing{\textbf{Supplementary Material} \\ \medskip Spatiotemporal modeling of \emph{Mycobacterium tuberculosis} transmission risk in a South African primary care clinic using environmental, clinical, and patient movement data}

### 2024-04-18 doc/paper/supplements.tex

\begin{figure}[!htpb]
    \centering
    \includegraphics{results/inputs/bacterial-inactivation-rate.png}
    \caption{Prior distribution (log scale) for the bacterial inactivation rate (quanta h$^{-1}$) of \emph{Mtb} along with reported estimates from the literature\cite{Loudon1969AMRRD,Gannon2007ResVetSci,Klein2014IJ,Lever2000LettersAppliedMicrobioMyco}.}
    \label{fig:lambda-distribution}
\end{figure}

@@

Undiagnosed (subclinical) TB patients may go undetected because they do not show symptoms according to the WHO 4-question symptom screen (cough, fever, weight loss, and night sweats), or the diagnosis could not be made at first presentation based on existing tests\cite{Patterson2023Preprint}. Previous studies suggest that the number of undiagnosed (subclinical) TB patients is roughly similar to the number of diagnosed TB patients\cite{Berhanu2023CID,Moyo2022LancetID}. Therefore, we model the number of undiagnosed TB patients with a Multinomial distribution based on the counts of the daily number of diagnosed TB patients during our study period from October to November 2021 (\Cref{fig:undiagnosed-distribution}. We assume that all clinic attendees can be potential undiagnosed TB patients and sample among them with equal probability. We further assume that undiagnosed and diagnosed TB patients have the same quanta generation rate.

@@

>>>>

\begin{figure}[!htpb]
    \centering
    \includegraphics{results/inputs/bacterial-inactivation-rate.png}
    \caption{Prior distribution (log scale) for the bacterial inactivation rate (quanta h$^{-1}$) of \emph{Mtb} along with reported estimates from the literature\cite{Loudon1969AMRRD,Gannon2007ResVetSci,Klein2014IJMyco,Lever2000LettersAppliedMicrobio}.}
    \label{fig:lambda-distribution}
\end{figure}

@@

Undiagnosed (subclinical) TB patients may go undetected because they do not show symptoms according to the WHO 4-question symptom screen (cough, fever, weight loss, and night sweats), or the diagnosis could not be made at first presentation based on existing tests\cite{Patterson2024PNAS}. Previous studies suggest that the number of undiagnosed (subclinical) TB patients is roughly similar to the number of diagnosed TB patients\cite{Berhanu2023CID,Moyo2022LancetID}. Therefore, we model the number of undiagnosed TB patients with a Multinomial distribution based on the counts of the daily number of diagnosed TB patients during our study period from October to November 2021 (\Cref{fig:undiagnosed-distribution}. We assume that all clinic attendees can be potential undiagnosed TB patients and sample among them with equal probability. We further assume that undiagnosed and diagnosed TB patients have the same quanta generation rate.

@@

\section{Additional results}\label{sec:additional-results}

\begin{figure}[!htpb]
    \centering
    \includegraphics{results/data/diagnosed-tb-patients.png}
    \caption{Number of diagnosed TB patients (dark bars) and those suspected of TB (light bars) following symptom screening. Modeled study days in color, other clinic days in October and November in grey.}
    \label{fig:diagnosed-tb-patients}
\end{figure}

\begin{figure}[!htpb]
    \centering
    \includegraphics{results/data/co2-levels-over-time.png}
    \caption{CO$_2$ levels per room of the clinic over time per day.}
    \label{fig:co2-levels}
\end{figure}

\begin{figure}[!htpb]
    \centering
    \includegraphics{results/modeling/mean-roi-assumptions.png}
    \caption{\textbf{Scenario modeling results.} Mean risk of infection per clinical attendee if \textbf{(a)}~the number of infectious people in the clinic corresponded to the prevalence of TB in the population, or \textbf{(b)}~the number of infectious people in the clinic corresponded to the number of bacteriologically confirmed TB patients and those suspected of having TB due to respiratory symptoms when attending the clinic. Low: <5\%, Medium: 5-10\%, High: >10\% risk of infection.}
    \label{fig:assumptions-results}
\end{figure}
